---
title: "Xling analysis"
author: "Gladys Baudet"
date: "16/05/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Retrieve freq_words



```{r freq_words, echo=FALSE, eval=TRUE}
library(dplyr)
library(lme4)
library(lmerTest)
library(ggplot2)


##### PATHS TO MODIFY ON YOUR COMPUTER ###########
load("/Users/gladysbaudet/Desktop/PFE/scripts/uni_joined.Rdata")
load("/Users/gladysbaudet/Desktop/PFE/CDI/uni_joined_no_slash.Rdata")

path = "/Users/gladysbaudet/Desktop/PFE/Results/"
##################################################


corpora <- c("Danish/Plunkett/", "French/Lyon/", "Spanish/OreaPine/", "Swedish/Lund/")
algos <- c("ag/", "dibs/", "puddle/", "tp/relativeforward/", "tp/relativebackward/", "tp/absoluteforward/", "tp/absolutebackward/", "baseline0/", "baseline1/") #baseline0, baseline1
units <- c("phoneme/", "syllable/")
#languages <- c("English (American)", "Danish", "French (French)", "Spanish (European)", "Swedish")
languages <- c("English (American)", "Danish", "French (French)", "Spanish (European)", "Swedish")

```

```{r laplace}
laplace_smoothing <- function(df){
  total=sum(df["count"])
  #print(total)
  size=nrow(df)
  #print(size)
  df$laplace_smoothing<-df$count+1
  df$laplace_smoothing<-df$laplace_smoothing/(total+size)
  return(df)
}
```

```{r english, echo=TRUE, eval=TRUE}
corpus <- "English/Brent/"
lang <- "English"
data <- c()

# first, gold english
gold = read.csv(paste(path, corpus, "gold_freq_words.csv", sep=''), sep="")
colnames(gold) <- c("count", "words")
gold$language <- lang
gold$au <- "gold"
#random choice
#gold$unit <- "syllable"

# add gold to data
gold <- laplace_smoothing(gold)
data <- rbind(data, gold)

for (algo in algos){
  print(algo)
  for (unit in units){
    # read new freq_words
    curr = read.csv(paste(path, corpus, algo, unit, "freq-words.txt", sep=''), sep="")
    colnames(curr) <- c("count", "words")
    # merge with gold, keeping all words from gold (should we remove count.x ?)
    new_curr <- merge(gold, curr, by="words", all.x=TRUE)
    drop = c("count.x")
    new_curr <- new_curr[, !(names(new_curr) %in% c("count.x"))]
    names(new_curr)[names(new_curr) == 'count.y'] <- 'count'
    new_curr$au <- paste(algo, unit, sep='')
    #new_curr$unit <- unit
    
    # laplace smoothing
    new_curr[is.na(new_curr)] <- 0
    new_curr <- laplace_smoothing(new_curr)
    # add to data
    data <- rbind(data, new_curr)
  }
}

```


```{r other}
for (corpus in corpora){
  lang <- strsplit(corpus, '/')[[1]][1]
  print(lang)
  # read gold
  gold = read.csv(paste(path, corpus, "gold_freq_words.csv", sep=''), sep="")
  colnames(gold) <- c("count", "words")
  gold$language <- lang
  gold$au <- "gold"
  #random choice
  #gold$unit <- "syllable"
  
  #add gold
  gold <- laplace_smoothing(gold)
  data <- rbind(data, gold)
  
  for (algo in algos){
    print(algo)
    for (unit in units){
      # read segmented
      curr = read.csv(paste(path, corpus, algo, unit, "freq_words.csv", sep=''), sep="")
      colnames(curr) <- c("count", "words")
      #merge with gold (+remove goldcount column, rename count column)
      new_curr <- merge(gold, curr, by="words", all.x=TRUE)
      new_curr <- new_curr[, !(names(new_curr) %in% c("count.x"))]
      names(new_curr)[names(new_curr) == 'count.y'] <- 'count'
      
      new_curr$au <- paste(algo,unit, sep='')
      #new_curr$unit <- unit
      
      # laplace smoothing here?
      new_curr[is.na(new_curr)] <- 0
      new_curr <- laplace_smoothing(new_curr)
      data <- rbind(data, new_curr)

    
    }
  }
}
      
      
  
```


## Statistics on CDI
Number of words per report in each language

```{r cdi-stats}

for (lang in languages){
  cdi_lang <- uni_joined %>% filter(language==lang, age==12, measure=="understands")
  print(lang)
  print(nrow(cdi_lang))
}

```

Age at which mean number of reports is higher

```{r cdi-stats2}
for (a in seq(8,18,2)){
  s=0
  for (lang in languages){
    cdi_lang <- uni_joined %>% filter(language==lang, age==a, measure=="understands")
    s <- s+cdi_lang$num_false[1]+cdi_lang$num_true[1]
    
  }
  print(paste(a,s,sep="  "))
  print(s)
}

```

Number of reports and mean understanding at chosen age
```{r cdi-stats3}

  for (lang in languages){
    cdi_lang <- uni_joined %>% filter(language==lang, age==12, measure=="understands")
    print(lang)
    print(paste(cdi_lang$num_false[1]+cdi_lang$num_true[1], mean(cdi_lang$prop), sep="  "))
  }


```

### Compare CDI (Quebec/France, Mexico/Spain)

```{r load_words}
fr = read.csv("/Users/gladysbaudet/Desktop/PFE/CDI/french/full_cdi_WG.csv")
sp = read.csv("/Users/gladysbaudet/Desktop/PFE/CDI/spanish/full_cdi_WG.csv")
fr <- fr %>% filter(age==12, type=="word")
sp <- sp %>% filter(age==12, type=="word")
```

```{r compare_words}
fr_words$words <- unique(fr$definition)
fr_words$words2 <- unique(fr$definition)
sp_words$words <- unique(sp$definition)

fr_aoa <- uni_joined %>% filter(language=="French (Quebec)", measure=="understands", age==12)
sp_aoa <- uni_joined %>% filter(language=="Spanish (Mexican)", measure=="understands", age==12)



fr_inter <- merge(fr_words[c("words","words2")], fr_aoa[c("words","lexical_classes")], by="words", all.y=TRUE)

fr_inter2 <- merge(fr_words, fr_aoa, by="words")
sp_inter <- merge(sp_words, sp_aoa, by="words")



print(paste("fr", "local",length(fr_words$words), "aoa", nrow(fr_aoa), "inter", nrow(fr_inter2), sep=" "))
print(paste("sp", "local",length(sp_words$words), "aoa", nrow(sp_aoa), "inter", nrow(sp_inter), sep=" "))
```


## Using other CDI (uni_joined for English, Danish, Swedish, other for French, Spanish)

```{r sep_/}
dup_rows <- function(df){
  to_modif <- df[grep("/", df$words),]
  to_modif <- rbind(to_modif, df[grep(",", df$words),])
  to_modif <- rbind(to_modif, df[grep("(.*)", df$words),])
  to_modif_new <- c()
  
  for (i in 1:nrow(to_modif)){
    
    row <- to_modif[i,]
    if(i==1){
      print(row[["words"]])
    }
    word <- as.character(row[["words"]])
    word <- unlist(strsplit(word, "/"))[1]
    word <- unlist(strsplit(word, ","))[1]
    word <- unlist(strsplit(word, "[(]"))[1]
    new_row1 <- row
    #new_row2 <- row
    new_row1["words"] <- word
    #new_row2["words"] <- word[2]
    if(i==1){
      print(new_row1)
    }
    to_modif_new <- rbind(to_modif_new,new_row1)
    #to_modif_new <- rbind(to_modif_new,new_row2)
  }
  
  df_res <- anti_join(df, to_modif, c("language", "words", "age"))
  df_res <- rbind(df_res, to_modif_new)
  df_res <- df_res[df_res$words!="",]
  return(df_res)
}
```

Clean AOA CDI in English, Danish and Swedish

```{r clean_cdi_en_da_sw}

en_da_sw <- uni_joined[c("language", "age", "prop", "measure", "words")]
en_da_sw <- en_da_sw %>% filter(language %in% c("English (American)", "Danish", "Swedish"), measure=="understands")
en_da_sw <- en_da_sw[c("language", "age", "prop", "words")]

en_da_sw_clean <- dup_rows(en_da_sw)


```

Retrieve data in Spanish (European) and French (French)

```{r sp_fr}
fr <- read.csv("/Users/gladysbaudet/Desktop/PFE/CDI/french/WG_prop_French_FR.csv")
## rename columns
names(fr)[names(fr) == 'Type'] <- 'words'
fr <- fr[c("age", "prop", "words")]
fr$language <- "French (French)"

sp <- read.csv("/Users/gladysbaudet/Desktop/PFE/CDI/spanish/WG_prop_Spanish_European.csv")
## rename columns
names(sp)[names(sp) == 'Type'] <- 'words'
sp <- sp[c("age", "prop", "words")]
sp$language <- "Spanish (European)"

sp_fr <- rbind(sp, fr)



sp_fr <- sp_fr[c("language", "age", "prop", "words")]
sp_fr_clean <- dup_rows(sp_fr)

```

Join both

```{r join_cdi}
cdi_all <- rbind(en_da_sw_clean, sp_fr_clean)

```

## Merge CDS/CDI

Merging on type and language.

```{r merge, echo=FALSE, eval=TRUE}

#data$language[data$language=="English"] <- "English (American)"
#data$language[data$language=="French"] <- "French (French)"
#data$language[data$language=="Spanish"] <- "Spanish (European)"
#cds_data <- data
#full_df <- merge(data, uni_joined, by=c("language", "words"))
#full_df_new <- merge(data, uni_joined_new, by=c("language", "words"))

load("/Users/gladysbaudet/Desktop/PFE/scripts/cds_res.Rdata")
data$language[data$language=="English"] <- "English (American)"
data$language[data$language=="French (Quebec)"] <- "French (French)"
data$language[data$language=="Spanish (Mexican)"] <- "Spanish (European)"
cds_data <- data

mixed_df <- merge(data, cdi_all, by=c("language","words"))
mixed_df$au = factor(mixed_df$au)
mixed_df$language = factor(mixed_df$language)
mixed_df$au = relevel(mixed_df$au, "gold")
mixed_df$language = relevel(mixed_df$language, "English (American)")

```

```{r save}
save(cds_data, file="/Users/gladysbaudet/Desktop/PFE/scripts/cds_res.Rdata")
save(mixed_df, file="/Users/gladysbaudet/Desktop/PFE/scripts/all_res.Rdata")
```

## Select one age

Which one ? 16 month has max average number of reports

```{r merge2, echo=FALSE, eval=TRUE}

data_16 <- full_df %>% 
  filter(age=='16')

data_16$language=factor(data_16$language)
data_16$language=relevel(data_16$language, "English (American)")
data_16$au=factor(data_16$au)
data_16$au=relevel(data_16$au, "gold")

```


## Actual analysis

### Check english results

```{r analysis}


fit0=lm(prop~log(laplace_smoothing), data=data_16 %>% filter(language=="English (American)", au=="gold", measure=="understands"))
summary(fit0)
fit1=lm(prop~laplace_smoothing, data=data_16 %>% filter(language=="English (American)", au=="gold", measure=="understands"))
#summary(fit1)
fit2=lm(prop~count, data=data_16 %>% filter(language=="English (American)", au=="gold", measure=="understands"))
#summary(fit2)
fit3_b=lm(prop~log(count+1), data=data_16 %>% filter(language=="English (American)", au=="gold", measure=="understands"))
#summary(fit3_b)
fit3=lm(prop~log(count+1), data=data_16 %>% filter(language=="English (American)", au=="tp/relativebackward/syllable/", measure=="understands"))


```

```{r r2}
A_syll=paste(algos,"syllable/", sep="")
A_ph=paste(algos,"phoneme/", sep="")
A=c(A_syll, A_ph)
for (a in A)
{
  m=lm(prop~log(laplace_smoothing), data=data_16 %>% filter(language=="English (American)", au==a, measure=="understands"))
  print(paste( a, summary(m)$r.squared, sep=" :  "))
  }

```
### Question 1

One model, all languages, only gold

```{r q1_all_lang.compared_gold}

q1_data <- data_16 %>% filter(au=='gold', measure=="understands")
q1_data$language=factor(q1_data$language)
q1_data$language=relevel(q1_data$language, "English (American)")
fit_q1=lmer(prop~log(laplace_smoothing)+log(laplace_smoothing):language+(1+log(laplace_smoothing)|uni_lemma),q1_data)
summary(fit_q1)
```

One language, only gold 

```{r by_lang.compared_gold}
for(lang in languages){
  #lang <- "Danish"
  print(lang)
  #q12_data=data_16 %>% filter(language==lang, measure=="understands", au=="gold")
  #q12_data <- full_df %>% filter(language==lang, measure=="understands", au=="gold", age==12)
  q12_data <- mixed_df %>% filter(language==lang, au=="gold", age==13)
  print(nrow(q12_data))
  q12_data$au=factor(q12_data$au)
  #q12_data$au=relevel(q12_data$au, "gold")

  fit_q12=lm(prop~log(laplace_smoothing), q12_data)
  print(summary(fit_q12)$r.squared)
}
```

Using duplicated rows

```{r duprows}
#data_q13 <- full_df_new %>% filter(age==12, au=="tp/relativeforward/syllable/", measure=="understands")
data_q13 <- mixed_df %>% filter(age==12, au=="baseline0/syllable/")
for(lang in languages){
  print(lang)
  cur_dat <- data_q13 %>% filter(language==lang)
  print(nrow(cur_dat))
  fit_q13 <- lm(prop~log(laplace_smoothing), cur_dat)
  print(summary(fit_q13)$r.squared)
  plot(log(cur_dat$laplace_smoothing), cur_dat$prop, xlab="freq", ylab="prop", main=lang)
  abline(lm(prop ~ log(laplace_smoothing), cur_dat))
}
```

Using mixed df

```{r todo}

```

### Question 2 : across languages


Using mixed df - get all R2 (! age may change between languages !)
```{r todo2}

A_syll=paste(algos,"syllable/", sep="")
A_ph=paste(algos,"phoneme/", sep="")
A=c(A_syll, A_ph)
A=c("gold",A)
R2_res <- c()

for (lang in languages){
  print(lang)
  for (a in A){
    #print(a)
    for (aa in seq(11,15)){
      u <- unlist(strsplit(a, "/"))
      uu <- u[[length(u)]]
      algo <- u[[1]]
      if(length(u)>2){
        algo <- paste(u[[1]], u[[2]], sep='/')
      }
      data_cur <- mixed_df %>% filter(au==a, language==lang, age==aa) # AGE !!#
      fit = lm(prop~log(laplace_smoothing), data_cur)
      R2_res <- rbind(R2_res, c(lang, a, as.numeric(as.character(summary(fit)$r.squared)), algo, uu, aa))
    }
  }
}

R2_res <- as.data.frame(R2_res)
names(R2_res)[names(R2_res) == 'V1'] <- 'language'
names(R2_res)[names(R2_res) == 'V2'] <- 'au'
names(R2_res)[names(R2_res) == 'V3'] <- 'r2_score'
names(R2_res)[names(R2_res) == 'V4'] <- 'algo'
names(R2_res)[names(R2_res) == 'V5'] <- 'unit'
names(R2_res)[names(R2_res) == 'V6'] <- 'age'

R2_res$r2_score <- as.numeric(as.character(R2_res$r2_score))

R2_res$algo <- as.character(R2_res$algo)
R2_res$algo[R2_res$algo=="tp/absolutebackward"] <- ".BTPa"
R2_res$algo[R2_res$algo=="tp/absoluteforward"] <- ".FTPa"
R2_res$algo[R2_res$algo=="tp/relativebackward"] <- ".BTPr"
R2_res$algo[R2_res$algo=="tp/relativeforward"] <- ".FTPr"
R2_res$algo[R2_res$algo=="baseline0"] <- "b0"
R2_res$algo[R2_res$algo=="baseline1"] <- "b1"

```

```{r table_display_r2}
for (lang in language){
  for(u in units){
    for(a in algos){
      
    }
  }
}
```


```{r save_r2_res}

save(R2_res, file="/Users/gladysbaudet/Desktop/PFE/CDI/xling_r2_res.Rdata")
```


```{r display_r2}

ggplot(R2_res %>% filter(age==14), aes( x=algo, y=r2_score, color=language, shape=unit))+
  #geom_bar(stat="identity")+
  geom_point()+
  facet_grid(~language, scales="fixed")+
theme(axis.text.x=element_text(angle = -50, hjust = 0))
  

```

```{r by_lang.by_algo}
# create table lang.algo

# create au labels
A_syll=paste(algos,"syllable/", sep="")
A_ph=paste(algos,"phoneme/", sep="")
A=c(A_syll, A_ph)
A=c("gold",A)
res <- c()
for(lang in languages){
  res_lang <- c()
  for(a in A){
    data_cur=data_16 %>% filter(language==lang, au==a, measure=="understands")
    fit=lm(prop~log(laplace_smoothing), data_cur)
    res_lang <- c(res_lang, summary(fit)$r.squared)
  }
  res <- c(res, res_lang)
}

res_matrix <- matrix(res, ncol=length(A), byrow = TRUE)
colnames(res_matrix) <- A
rownames(res_matrix) <- languages
res_matrix <- data.frame(t(res_matrix))

print((res_matrix))

```

```{r by_lang.all_algos}

#for (lang in languages){
lang="Danish"
    data_cur <- data_16 %>% filter(language==lang, measure=="understands")
    fit <- lm(prop~log(laplace_smoothing)+log(laplace_smoothing):au, data_cur)
    summary(fit)
#}

```



```{r}
lang="English (American)"
#for(lang in languages) {
data_cur <- full_df %>% filter(age==13, au %in% c("gold", "tp/relativeforward/syllable/"), language==lang, measure=="understands")
fit <- lm(prop~log(count+1)+log(count+1):au, data_cur)
summary(fit)

#}
```




```{r full_model?, eval=FALSE}
library(lmerTest)
fit1=lmer(prop~log(laplace_smoothing)+log(laplace_smoothing):language++log(laplace_smoothing):au + (1 | uni_lemma),data=data_16 %>% filter(measure=="understands"))
summary(fit1)
```











